Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-09-12 latex/paper.tex
minor edits

\subsection{Applications}
This section describes the applications used to benchmark Dask and Spark.
We use three simple synthetic applications to have a deep understanding of the 
underlying behavior of the applications with simple I/O patterns, namely
\textit{Increment}, \textit{Multi-Increment}, and \textit{Histogram}.
Also, two neuroimaging applications are used to study more realistic 
applications, namely \textit{Kmeans} and \textit{BIDS App Example}{\cite{gorgolewski2017bids}}.
\HL{
	We chose these neuroimaging data processing applications to study the 
	effects of various Big Data characteristics.
	Table~{\ref{table:applications}} depicts the Big Data characteristics used in
	each application. 
	Each row represents an application, while each column represents an engine's characteristic.
	The \textit{Map} and \textit{Reduce} represent the Map-Reduce paradigm operations,
	and the \textit{Shuffle} column represents the amount of data shuffled between stages if any.
	The column \textit{Dataset in-memory} depicts whether the whole dataset is required to 
	be in memory for processing.
	Then \textit{Compute intensive} and \textit{Data intensive} shows if the applications are
	compute or data intensive.
	Lastly, the \textit{Containerized} column shows applications wrapped in a container.
}

@@

>>>>

\subsection{Applications}
This section describes the applications used to benchmark Dask and Spark.
We use three simple synthetic applications to have a deep understanding of the 
underlying behavior of the applications with simple I/O patterns, namely
\textit{Increment}, \textit{Multi-Increment}, and \textit{Histogram}.
Also, two neuroimaging applications are used to study more realistic 
applications, namely \textit{Kmeans} and \textit{BIDS App Example}{\cite{gorgolewski2017bids}}.
\HL{
	We chose these neuroimaging data processing applications to study the 
	effects of various Big Data characteristics.
	Table~{\ref{table:applications}} depicts the Big Data characteristics used in
	each application. 
	In this table, \textit{Map} and \textit{Reduce} represent the Map-Reduce paradigm operations,
	and the \textit{Shuffle} column represents the amount of data shuffled between stages if any.
	The column \textit{Dataset in-memory} depicts whether the whole dataset is required to 
	be in memory for processing.
	Then \textit{Compute intensive} and \textit{Data intensive} shows if the applications are
	compute or data intensive.
	Lastly, the \textit{Containerized} column shows applications wrapped in a container.
}

@@

\HL{
	Due to the limited amount of benchmarks available to evaluate the performance
    of neuroimaging applications, we use our own collection of applications.
    Further efforts would be needed to create a credible and in-depth performance
    benchmark specific to the neuroimaging field.
}
